---
title: "R Notebook"
output: html_notebook
# runtime: shiny
---

### Equations

You can use LaTeX:

$${\displaystyle \mathbf {X} =\mathbf {U} \mathbf {\Sigma } \mathbf {W} ^{T}}$$

where $\mathbf {\Sigma }$ is a diagonal matrix with singular values of $\mathbf {X}$


### Plots


```{r}
library(ggplot2)
df = data.frame(x=c(1, 2, 2, 3))
ggplot(df, aes(x=x)) + geom_density(fill='#59A14F')
```


### Fasta

```{r}
# install.packages("msaR")
library(msaR)
seqfile <- system.file("sequences", "AHBA.aln", package="msaR")
msaR(seqfile)

```

### Molecular structures

Using [r3dmol](https://github.com/swsoyee/r3dmol). In development.

```{r}
# install.packages("r3dmol")
library(r3dmol)
r3dmol() %>%
  m_add_model(data = pdb_6zsl, format = "pdb") %>%
  m_zoom_to() %>%
  m_set_style(style = list(cartoon = list(color = 'spectrum')))
```



### Imaging data

Embedding 3D images in notebooks is possible, but does not always work.

```{r, echo=FALSE}
# sudo apt install libglu1-mesa-dev freeglut3-dev mesa-common-dev
# install.packages("nat")
# library(nat)
# brain = read.nrrd('data/005_32months_T2_RegT1_Reg2Atlas_ManualBrainMask_Stripped.nrr')
# open3d()
# plot3d(brain)
```


### Networks and pathways

There are multiple ways to communicate with cytoscape from R. Either static images can be embedded, or interactive plots can be served with shiny.

- cyjShinyOutput
- KEGGscape
- RC3


### Custom widget

Custom widgets can be created using shiny:

```{r echo=FALSE}
library(shiny)
sliderInput("m", h3("m"), min=-2, max=2, value=0, step=0.01)
sliderInput("b", h3("b"), min=-3, max=3, value=0, step=0.5)

renderPlot({
  m = input$m
  b = input$b
  x = seq(-100, 100) / 10
  df = data.frame(x=x, y=m * x + b)
  (
    ggplot(df, aes(x=x, y=y))
    + geom_point()
    + coord_fixed()
    + ylim(-10, 10)
  )
})
```

### Multi-lingual - bash example

Change the language identifier to use bash:

```{bash}
pwd
```

Create a file with one word *test*:

```{bash}
echo "test" > test.txt
```

md5sum is a simple command which you can run on Linux (md5 on Mac) to get a *short* reproducible string which will *very likely* change significantly if the file contents changes.

```{bash}
md5sum test.txt
```

If we change it slightly:

```{bash}
echo "test2" > test.txt
md5sum test.txt
```

If we revert back:

```{bash}
echo "test" > test.txt
md5sum test.txt
```


### Multi-lingual - Python inside R

```{python, python.reticulate = FALSE}
print("Hello word!")
```